\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-01 tex/paper.tex
Playing around with the model

%{{{
\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}

@@

@@

\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        u \in U \text{ can delete } m \in c & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\begin{equation} \label{eq:fileupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        x  & = f \in m' \land \\
        f' & = u, change(x) \land \\
        u, & write(f') \land \\
        u, & modify(f', m) \Implies f \in F \land f' \in F
    \end{split}
\end{equation}
If a user wants to update a file in a content, the file is copied and the original is intact.

@@

\fix Add more findings
\newpage 
\section{Implementation} \label{sec:implementation} 
This chapter deals with the second part of this work, namely the implementation of the Perius
system. The implementation is based on the model described in Section~\ref{sec:model}. As this work
is not intended as an instructions manual, more information about how to deploy and use Perius can
be found on \url{http://perius.se}. This chapter's focus is instead on how the decisions for the
implementation were made, how well the system would scale and the resulting security implications.

@@

\subsubsection{Examples of Copy-on-Write system implementations}
\subsubsubsection{BTRFS}
Btrfs is a B-tree file system for Linux which makes use of Copy-on-Write to make it able to do
efficient writeable snapshots and clones. It also supports cloning of subtrees without having to
actually copy the whole subtree, this is due to the Copy-on-Write effect. As several nodes in the
tree can refer to the same node each node keeps track of how many parents it has by a reference
counter so that the node can be deallocated once the node does not have any parents any more. The
reference counter is not stored in the nodes themselves but rather in a separate data structure so
that a node's counter can be modified without modifying the node itself and therefore eludes the
Copy-on-Write that would have to occur.

>>>>

%{{{
\documentclass[a4paper,12pt]{article}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{float}
\usepackage{sectsty}
\usepackage{pdfpages}
\usepackage[section]{placeins}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{setspace}
\usepackage[toc,page]{appendix}
\usepackage{framed}
\usepackage{geometry}
\usepackage{extarrows}
\usepackage{mathpartir}

@@

This work has taken a lot inspiration from the way BTRFS~\cite{BTRFS} handles snapshots, which is
further explained in Section~\ref{sec:btrfs}.

@@

\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        u \in U \text{ can delete } m \in c & \Iff u \in A[u,c] \text{ and read-only } \notin c \\
        \forall c \in C, \nexists u \in U & \text{ can delete } f \in c
    \end{split}
\end{equation}

@@

\begin{equation} \label{eq:fileupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        f  & = f \in m' \land \\
        f' & = u, change(f) \land \\
        u, & write(f') \land \\
        u, & modify(f', m) \Implies f \in F \land f' \in F
    \end{split}
\end{equation}
\begin{equation}
    \begin{split}
        (F, f \in c) \xrightarrow{update(f', c)} (\{f, f'\} \subset F, f' \in c) 
    \end{split}
\end{equation}
\inferrule
{f \in c \xrightarrow{update(f', c)} f' \in c }
{c \cap \{f\} \\ c \cup \{f'\} \\ F \cup \{f, f'\}}

\vspace{2em}

\inferrule
{f \in c \\ update(f', c) \\ f' \in c}
{F \cup \{f, f'\}}

\vspace{2em}

\inferrule
{f \in F \\ [fileId = f.id, \dots] \in C \\ f \neq f'} 
{F \cup \{f\} \xrightarrow{write(fileId, f'.id)} F \cup \{f, f'\}}

\vspace{2em}
If a user wants to update a file in a content, the file is copied and the original is intact.

@@

\subsubsection{JPF Results}
Although the JPF model checking results did not return any errors or showed any possible misbehaviours
of the model, it should not be considered proven. The results however strongly indicate that there are no
major flaws in it. But as the model will be more complicated once fully implemented as an application
there might be flaws in the implementation details.

\newpage 
\section{Implementation} \label{sec:implementation} 
This chapter deals with the second part of this work, namely the implementation of the Perius
system. The implementation is based on the model described in Section~\ref{sec:model}. As this work
is not intended as an instructions manual, more information about how to deploy and use Perius can
be found on \url{http://perius.se}. This chapter's focus is instead on how the decisions for the
implementation were made, how well the system would scale and the resulting security implications.

@@

\subsubsection{Examples of Copy-on-Write system implementations}
\subsubsubsection{BTRFS} \label{sec:btrfs}
Btrfs is a B-tree file system for Linux which makes use of Copy-on-Write to make it able to do
efficient writeable snapshots and clones. It also supports cloning of subtrees without having to
actually copy the whole subtree, this is due to the Copy-on-Write effect. As several nodes in the
tree can refer to the same node each node keeps track of how many parents it has by a reference
counter so that the node can be deallocated once the node does not have any parents any more. The
reference counter is not stored in the nodes themselves but rather in a separate data structure so
that a node's counter can be modified without modifying the node itself and therefore eludes the
Copy-on-Write that would have to occur.
